SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-30 docs/questioning.tex
work on policy enforcement

@@

In this method, developers must define
specific security policies on the server side.
Then the policies are enforced either in the user's
browser at runtime or in a server-side proxy that
intercepts server responses.

@@

@@

  \multirow{4}{*}{{\sc isr}}

@@

	\multirow{10}{*}{Policy Enforcement}

@@

  \multirow{1}{*}{Hybrid}

>>>>

This approach is used to detect attacks that target web users.
When using a framework that implements
this approach, developers must define
specific security policies on the server side.
Then the policies are enforced either in the user's
browser at runtime or in a server-side proxy that intercepts
server responses. Policy enforcement is one of the two
approaches (the other is Securing Mashups) that is
used to prevent {\sc csrf} attacks.

A number of the frameworks define policies
based on information and features provided by
the Document Object Model ({\sc dom}) of a web page.
Specifically, developers must place all legitimate
scripts inside {\sc html} elements like {\tt div}.
The web browser (locus {\sc x}), parses the
{\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts
are treated according to the policies defined
on the server. Frameworks that support the
above functionality are {\sc beep}~\cite{TNH07}
and {\sc dsi}~\cite{NSS06}.
The main problem with the above mechanisms is
that they are vulnerable to non-persistent {\sc xss}
attacks that alter the {\sc dom} of an already rendered
page\footnote{\url{https://www.owasp.org/index.php/DOM_Based_XSS}}
~\cite{APKLM10}.

% There are also frameworks that introduce
% policies directly in the scripts that exist in the server.

% controlling information flows: {\sc soma}~\cite{OWVS08}
% and Noxes~\cite{KKVJ06,KJKV09} (the client defines policies).

@@

@@

{\it Blueprint}~\cite{LV09}.

@@

@@

	\multirow{9}{*}{Policy Enforcement}

@@

  \multirow{3}{*}{Hybrid}
